Tweedie in TMB

### 2019-02-20 analysis/tweedie-TMB.Rmd
tweedie in TMB that runs!

```{r}
## Data and parameters
data <- list(x = x, y = y)
parameters <- list(a=0, b=0, power = 1.5, log_phi = log(1) )

@@

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr

```

# check against values are returned with glm
```{r}
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
```

>>>>

```{r}
## Data and parameters
data <- list(y = y, x = x)
parameters <- list(a=0, b=0, log_phi = log(1), p = 0 )

@@

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr
```

# find maximum likelihood using nlminb

```{r}
# function to generate negative log-likelihood for a parameter value
nll_tweedie <- function(par) {
  eta <- par[1] + par[2] * x
  mu <- exp(eta)
  p <- plogis(par[3]) + 1
  phi <- exp(par[4])
  # sum of negative log likelihoods:
  loglik <- log(dtweedie(y, power = p, mu = mu, phi = phi))
  nll <- -sum(loglik) #[is.finite(loglik)]
  print(nll)
  nll
}

tweedie_ml <- nlminb(start = c(a = 0, b = 0, ipx = 0, log_phi = log(1)), nll_tweedie)
tweedie_ml$par 
```

# check both methods against values are returned with glm
```{r}
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
sdr
tweedie_ml$par 
```
